Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-07 manuscript.tex
7 updates

When we tested the SN density fit to the CCFs provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method. By more sensitive, we mean here that the correlation between the skewness and either the mean or median of the SN density is stronger than between BIS SPAN and the mean of a Normal density. Moreover, the correlation between the FWHM and the CCF barycenter is also stronger when using the parameters from the SN compared to the parameters from the Normal. We also confirmed the behavior that the SN parameters are more correlated than the Normal parameters in the case where a planetary signal is added the to stellar activity modeled by SOAP 2.0.

>>>>

To analyze the performance the proposed SN framework, tests on both simulated and real data were carried out and compared to the usual approach of fitting a Normal density shape (for estimating the RV and FWHM) and the BIS SPAN (for estimating the asymmetry).
The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star. The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method. 
In this case, sensitivity was measured using the correlation between the asymmetry and the estimated RV's, and it turned out either SN mean RV or SN median RV had a stronger correlation with gamma than the correlation between N mean RV and BIS SPAN. 
Moreover, the correlation between the FWHM and the estimated RV's is also stronger when using the parameters from the SN compared to the parameters from the Normal. 
The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
